Upper Limits on CN from Falling Evaporating Bodies\\seen towards \bp{}

### 2023-01-09 src/tex/ms.tex
[showyourwork] overleaf sync

@@

Spectroscopic observations of Solar system comets when they are very close to the Sun are rare due to observational difficulties.
%
%The only comet spectroscopically observed closer than 0.2~au from the Sun is C/1965~S1 Ikeya-Seki.
%
%For this comet, it was noticed that the main emission bands/lines detected in its optical spectrum dramatically changed while the comet approached the Sun.
%
%At distances greater than 0.4~au, \ce{CH}, \ce{CN}, \ce{C2}, and \ce{C3} emission bands dominated the spectrum, but at 0.15 au from the Sun, the only molecular emission detected was \ce{CN}, while numerous atomic lines were visible \citep[\ce{[\ion{O}{i}], \ion{Na}{i}, \ion{K}{i}, \ion{Ca}{ii}, \ion{Cr}{i}, \ion{Mn}{i}, \ion{Fe}{i}, \ion{Ni}{i}, \ion{Cu}{i}, \ion{V}{i}; ][]{Dufay65,Thackeray1966,Preston1967,Slaughter1969}.

%While the above neutral/ionic signatures in FEBs are well established, it is important to note that detection of these species in Solar system comets is rare.
%
\ion{Ca}{ii} and \ion{Fe}{i} have only been spectroscopically observed via emission lines in the sun-grazing comet C/1965~S1 Ikeya-Seki.
%
For this comet, it was noticed that the main emission bands/lines detected in its optical spectrum dramatically changed while the comets approached the Sun.
%
At distances greater than 0.4~au, \ce{CH}, \ce{CN}, \ce{C2}, and \ce{C3} emission bands dominated the spectrum.
%
However, at 0.15~au from the Sun, the only molecular emission detected was \ce{CN}, while numerous atomic lines were visible \citep[\ion{[O]}{i}, \ion{Na}{i}, \ion{K}{i}, \ion{Ca}{ii}, \ion{Cr}{i}, \ion{Mn}{i}, \ion{Fe}{i}, \ion{Ni}{i}, \ion{Cu}{i}, \ion{V}{i}; ][]{Dufay65,Thackeray1966,Preston1967,Slaughter1969}.
%
Additionally, a tail of \ion{Fe}{i} atoms was proposed to explain a linear feature imaged in the tail of sungrazing comet C/2016~P1 McNaught 2006P1 \citep{Fulle2007}.

On the other hand, \ion{Na}{i} D-line emission has been observed in many comets within $r \sim 1$ au of the Sun, where either the emission was much brighter than the foreground sky emission, or the comet was observed at high spectral resolution enabling separation from the telluric lines [REFs].
%
The high efficiency of the \ion{Na}{i} D transition makes it easily detectable, even for relatively low column density.
%
A notable discovery was a spectacular tail of \ion{Na}{i} associated with comet C/1995 O1 Hale-Bopp at $r\sim 1$ au, formed by radiation pressure on the neutral atoms before ionisation \citep{Cremonese1997}.

>>>>

The formation and evolution of planets and their attendant moons is thought to occur in the first few ten million years of the stellar system \hl{REF}.
%
Comets deliver volatiles across menay different distances within the Solar system, from the outermost reaches of the Oort cloud in to the terrestrial planets.
%
It is therefore important to understand the distribution, nature and chemical composition of exocomets in other planet forming systems.

One of the closest young systems is Beta Pictoris, which has been studied intensively both with direct imaging and with spectroscopy.

Beta Pictoris is a young, early type star whose stellar chromosphreic lines show rotational broadening of 200 km/s \hl{REF}.
%
Additional, much narrower absorption features are seen in the Calcium H and K lines.
%
These features appear and disappear on several hour long timescales, and show a different range of morphologies \hl{[REF]}.
%
Intensive spectroscopic monitoring over several hours show changes of radial velocity of these components consistent with elliptical orbits.
%
The absorption is hypothesised to be due to the evaporation of infalling bodies that pass within a few stellar radii of the star, resulting in sublimation of metals that produce a large coma containing the Calcium atoms which are then seen as an additional absorption component \hl{[REF REF]}.

From the multiple detections of exocomets in spectroscopy towards Beta Pictoris, the broadband detection of exocomet tails transiting a star were seen initially detected towards the star KIC~3542116 \citep{Rappaport18} with the Kepler satellite [REF] and subsequently detected in TESS data towards Beta Pictoris \citep{Zieba19}.
%
Observations of Beta Pictoris in subsequent TESS sector revealed over two dozen transits whost depth follows a power law distribution similar to those of the Solar system \citep{LecavelierdesEtangs22,Pavlenko22}.

@@

Spectroscopic observations of Solar system comets when they are very close to the Sun are rare due to observational difficulties.
%
%The only comet spectroscopically observed closer than 0.2~au from the Sun is C/1965~S1 Ikeya-Seki.
%
%For this comet, it was noticed that the main emission bands/lines detected in its optical spectrum dramatically changed while the comet approached the Sun.
%
%At distances greater than 0.4~au, \ce{CH}, \ce{CN}, \ce{C2}, and \ce{C3} emission bands dominated the spectrum, but at 0.15 au from the Sun, the only molecular emission detected was \ce{CN}, while numerous atomic lines were visible \citep[\ce{[\ion{O}{i}], \ion{Na}{i}, \ion{K}{i}, \ion{Ca}{ii}, \ion{Cr}{i}, \ion{Mn}{i}, \ion{Fe}{i}, \ion{Ni}{i}, \ion{Cu}{i}, \ion{V}{i}; ][]{Dufay65,Thackeray1966,Preston1967,Slaughter1969}.
%%\ion{Ca}{ii} and \ion{Fe}{i} have only been spectroscopically observed via emission lines in the sun-grazing comet C/1965~S1 Ikeya-Seki.
%
For this comet, it was noticed that the main emission bands/lines detected in its optical spectrum dramatically changed while the comets approached the Sun.
%
At distances greater than 0.4~au, \ce{CH}, \ce{CN}, \ce{C2}, and \ce{C3} emission bands dominated the spectrum.
%
However, at 0.15~au from the Sun, the only molecular emission detected was \ce{CN}, while numerous atomic lines were visible \citep[\ion{[O]}{i}, \ion{Na}{i}, \ion{K}{i}, \ion{Ca}{ii}, \ion{Cr}{i}, \ion{Mn}{i}, \ion{Fe}{i}, \ion{Ni}{i}, \ion{Cu}{i}, \ion{V}{i}; ][]{Dufay65,Thackeray1966,Preston1967,Slaughter1969}.
%
Additionally, a tail of \ion{Fe}{i} atoms was proposed to explain a linear feature imaged in the tail of sungrazing comet C/2016~P1 McNaught 2006P1 \citep{Fulle2007}.

On the other hand, \ion{Na}{i} D-line emission has been observed in many comets within $r \sim 1$ au of the Sun, where either the emission was much brighter than the foreground sky emission, or the comet was observed at high spectral resolution enabling separation from the telluric lines \hl{REFs}.
%
The high efficiency of the \ion{Na}{i} D transition makes it easily detectable, even for relatively low column density.
%
A notable discovery was a spectacular tail of \ion{Na}{i} associated with comet C/1995 O1 Hale-Bopp at $r\sim 1$ au, formed by radiation pressure on the neutral atoms before ionisation \citep{Cremonese1997}.
